\section{Introduction}
\subsection{Purpose}
This document aims to describe how the implementation and the integration testing took place.\\
The implementation is the last phase of the Dream application development cycle while testing is necessary in order to check if the critical parts on the application works correctly how described in the Design Document.
\\\\
Source code and releases could be found in the official project repository on GitHub (\href{https://github.com/matteovisotto/SE2-CecchettoSirianiVisotto}{https://github.com/matteovisotto/SE2-CecchettoSirianiVisotto}).

\subsection{Acronyms}

\subsubsection{Acronyms}
\begin{itemize}
    \item \textbf{API:} Application Programming Interface.
    \item \textbf{HTTPS:} Hyper Text Transfer Protocol over SSL.
    \item \textbf{DD:} Design Document.
    \item \textbf{TLS:} Transport Layer Security.
    \item \textbf{SSL:} Secure Socket Layer.
    \item \textbf{DBMS:} DataBase Management System.
    \item \textbf{IdP:} Identity Provider.
    \item \textbf{SP:} Service Provider.
    \item \textbf{RASD:} Requirements Analysis and Specification Document.
    \item \textbf{ACS:} Assertion Consumer Service .
    \item \textbf{SAML:} Security Assertion Markup Language.
    \item \textbf{DOM:} Document Object Model.
    \item \textbf{JPA:} Java Persistance API.
    \item \textbf{UI:} User Interface.
    \item \textbf{URL:} Uniform Resource Locator.
\end{itemize}

\subsection{Revision history}
\begin{itemize}
    \item v.1.0 - 06/02/2022
    \item v.1.1 - 11/02/2022 - Update installation instruction due to a typo.
\end{itemize}

\subsection{References}
\begin{itemize}
    \item Requirements Analysis Specification Document (RASD).
    \item Design Document(DD).
    \item Specification document: "R\&DD Assignment A.Y. 2021-2022".
    \item Official Data4Policy stakeholder's project repository: \href{https://github.com/UNDP-india/Data4Policy}{https://github.com/UNDP-india/Data4Policy}.
    \item Shibboleth documentation: \href{https://shibboleth.atlassian.net/wiki/home}{https://shibboleth.atlassian.net/wiki/home}.
    \item Meta RWI \href{https://dataforgood.facebook.com/dfg/tools/relative-wealth-index}{https://dataforgood.facebook.com/dfg/tools/relative-wealth-index}.
    \item ESRI Java geometry API: documentation: \href{https://github.com/Esri/geometry-api-java/wiki/}{https://github.com/Esri/geometry-api-java/wiki/}.
    \item Mailjet API documentation:  \href{https://github.com/mailjet/mailjet-apiv3-java}{https://github.com/mailjet/mailjet-apiv3-java}.
    \item Bootsrap 5 documentation:  \href{https://getbootstrap.com/docs/5.0/getting-started/introduction/}{https://getbootstrap.com/docs/5.0/getting-started/introduction/}.
    \item jQuery documentation:  \href{https://api.jquery.com/}{https://api.jquery.com/}.
    \item Thymeleaf documentation: \href{https://www.thymeleaf.org/documentation.html}{https://www.thymeleaf.org/documentation.html}.
    \item HTML documentation: \href{https://developer.mozilla.org/en-US/docs/Web/HTML}{https://developer.mozilla.org/en-US/docs/Web/HTML}
    \item JavaScript documentation: \href{https://devdocs.io/javascript/}{https://devdocs.io/javascript/}.
    \item MySQL documentation: \href{https://dev.mysql.com/doc/}{https://dev.mysql.com/doc/}.
    \item Shibboleth documentation: \href{https://shibboleth.atlassian.net/wiki/home}{https://shibboleth.atlassian.net/wiki/home}.
    \item Shibboleth IdP configuration: \href{https://github.com/ConsortiumGARR/idem-tutorials/blob/master/idem-fedops/HOWTO-Shibboleth/Identity\%20Provider/Fedora/HOWTO\%20Install\%20and\%20Configure\%20a\%20Shibboleth\%20IdP\%20v3.2.1\%20on\%20Linux\%20Fedora\%2024\%20Server\%20Edition\%20with\%20Apache2\%20\%2B\%20Jetty9.md}{Github link}.
    \item Shibboleth SP configuration: \href{https://github.com/ConsortiumGARR/idem-tutorials/blob/master/idem-fedops/HOWTO-Shibboleth/Service\%20Provider/Debian/HOWTO\%20Install\%20and\%20Configure\%20a\%20Shibboleth\%20SP\%20v3.x\%20on\%20Debian-Ubuntu\%20Linux.md}{Github link}.
    \item GeoJSON specification: \href{https://geojson.org/}{https://geojson.org/}.
\end{itemize}
